---
title: "p8105_hw1_ac4140"
author: "Arielle"
date: "9/17/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (tidyverse)
```

# Question 1 
   ##Created a data frame 
      **a random sample of size 8 from a standard normal distrubution
      ** a logical vector indicating whether elements of the sample greater than 0 
      ** a character vector of length of 8
      ** a factor vector of length 8, with 3 different factor "levels"
      **converted variables as numeric functions for the logical, character and vector varaibles 

```{r question 1.1}
set.seed (10)

hw1_df = tibble (
  norm_samp = rnorm (8),
  norm_samp_pos = (norm_samp > 0),
  vec_char = c("My", "name", "is",   "Arielle","this", "is", "homework", "one"),
  size_factor = factor (c("small", "small",  "small", "medium",  "medium", "medium", "large", "large"))
                        
)

mean(pull(hw1_df, norm_samp))
mean(pull(hw1_df, norm_samp_pos))
mean(pull(hw1_df, vec_char))
mean(pull(hw1_df, size_factor))
```
  ##The code gave a mean for norm_samp and norm_samp_pos because they are numerical values. This does not work for vec_char and size_factor because they are charactor and factor vectors.

  ## Created a new code chunk that found the mean of the numeric values for logical, character, and factor varaibles

```{r question 1.2}
mean(as.numeric(pull(hw1_df, norm_samp_pos)))
mean(as.numeric(pull(hw1_df, vec_char)))
mean(as.numeric(pull(hw1_df, size_factor)))

```
  ##The code for norm_samp_poss gives a value of 0.625 this is because the the logical varaible was able to be converted to a numeric one because the logical variables can be converted to 0 and 1. The code for vec_char has NA because there is no numerical variable for this variable. The code for size_factor gave a mean however there were NA produced.

  ## convert the logical vector to numeric, and multiply the random sample by the result 
  ## convert the logical vector to a factor, and multiply the random sample by the result  
  ##convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r question 1.3}
(as.numeric(pull(hw1_df, norm_samp_pos)))*(pull(hw1_df, norm_samp))
(as.numeric(pull(hw1_df, vec_char)))*(pull(hw1_df, norm_samp))
(as.numeric(pull(hw1_df, size_factor)))*(pull(hw1_df, norm_samp))
```

#Question 2 
  ## Created a new data frame that comprised of 
   x: a random sample of size 500 from a standard Normal distribution
   y: a random sample of size 500 from a standard Normal distribution
  A logical vector indicating whether x + y > 1
   A numeric vector created by coercing the above logical vector
   A factor vector created by coercing the above logical vector

```{r question 2.0}
set.seed (1234)

hw1_df2 = tibble (
  x = rnorm(500),
  y = rnorm(500),
  a = (x + y > 1)
)
  b = as.numeric(pull(hw1_df2, a))
  c = as.factor(pull(hw1_df2, a))

```
The data set `hw1_df2` has `r nrow(hw1_df2)`, and ncol `r ncol(hw1_df2)`
*The mean for x is `r mean(pull(hw1_df2, x))`,
*The median for x is `r median(pull(hw1_df2, x))`,
*The standard deviation for x is `r sd(pull(hw1_df2, x))`
*The proportion of cases for which x + y > 1 is  `r mean(pull(hw1_df2, a))` 

  ## Made a scatterplot of y vs x; color points using the logical variable (adding color = ... inside of aes in your ggplot code should help). Make a second and third scatterplot that color points using the numeric and factor variables, respectively, and comment on the color scales.

```{r question 2.1}
ggplot (hw1_df2, aes(x = x, y = y,  color = a)) + geom_point()
## In the first scatter plot it shows y vs x, the blue represent the values of x + y that are greater than 1. The pink represenst the values of x + y that are less than 1. 

ggplot (hw1_df2, aes(x = x, y = y, color = b)) + geom_point()
## In the second scatter plot it shows y vs x, the light blue are the values of x +y greater than 1 and the the black represents the values that x +y is less than 1. This graph is on a scale base and it shows the two extremes of 1 and 0.

ggplot (hw1_df2, aes(x = x, y = y, color = c)) + geom_point()
## In the third scatter plot it shows y vs x, the blue represent the values of x + y that are greater than 1. The pink represenst the values of x + y that are less than 1.The first and the third graphs show up as the same.  

ggplot (hw1_df2, aes(x = x, y = y,  color = a)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```
